\documentclass{article}
\usepackage{amsmath}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{multicol}
\setstretch{1.5}
\begin{document}
\begin{multicols}{2}

\section*{Tier 1}
1. Newton's Second Law (Force = Mass × Acceleration): \\
   \( F = m \cdot a \) \\
2. Work Done by a Force: \\
   \( W = F \cdot d \cdot \cos(\theta) \) \\
3. Kinetic Energy: \\
   \( KE = \frac{1}{2} \cdot m \cdot v^2 \) \\
4. Potential Energy (Gravitational): \\
   \( PE = m \cdot g \cdot h \) \\
5. Hooke's Law (Spring Force): \\
   \( F = k \cdot x \) \\
6. Pressure in a Fluid at Rest: \\
   \( P = \rho \cdot g \cdot h \) \\
7. Bernoulli's Equation (Incompressible, Steady Flow): \\
   \( P + \frac{1}{2} \cdot \rho \cdot v^2 + \rho \cdot g \cdot h = \text{constant} \) \\
8. Fluid Flow Rate (Continuity Equation): \\
   \( A_1 \cdot v_1 = A_2 \cdot v_2 \) \\
9. Ideal Gas Law: \\
   \( PV = nRT \) \\
10. Efficiency (Thermal): \\
    \( \eta = \frac{W_{\text{out}}}{Q_{\text{in}}} \) \\
11. First Law of Thermodynamics (Energy Conservation): \\
    \( \Delta U = Q - W \) \\
12. Stress: \\
    \( \sigma = \frac{F}{A} \) \\
13. Strain: \\
    \( \epsilon = \frac{\Delta L}{L} \) \\
14. Young's Modulus: \\
    \( E = \frac{\sigma}{\epsilon} \) \\
15. Shear Stress: \\
    \( \tau = \frac{F}{A} \) \\
16. Shear Strain: \\
    \( \gamma = \frac{\Delta x}{h} \) \\
17. Bending Stress (Simple Beam): \\
    \( \sigma = \frac{M \cdot c}{I} \) \\
18. Torsional Shear Stress (Circular Shaft): \\
    \( \tau = \frac{T \cdot r}{J} \) \\
19. Coulomb's Law (Electrostatic Force): \\
    \( F = \frac{k \cdot q_1 \cdot q_2}{r^2} \) \\
20. Ohm's Law (Electrical Circuits): \\
    \( V = I \cdot R \) \\
21. Magnetic Field Strength (Straight Wire): \\
    \( B = \frac{\mu_0 \cdot I}{2 \cdot \pi \cdot r} \) \\
22. Frequency (Simple Harmonic Motion): \\
    \( f = \frac{1}{T} \) \\
23. Centripetal Force: \\
    \( F_c = \frac{m \cdot v^2}{r} \) \\
24. Angular Velocity: \\
    \( \omega = \frac{\theta}{t} \) \\
25. Wave Speed (Propagation): \\
    \( v = f \cdot \lambda \) \\

\newpage
\vfill\eject
\section*{Tier 2}
1. Moment of Inertia (Rectangle about centroid): \\
   \( I = \frac{b \cdot h^3}{12} \) \\
2. Poisson's Ratio (Longitudinal to lateral strain): \\
   \( \nu = -\frac{\epsilon_{\text{lat}}}{\epsilon_{\text{long}}} \) \\
3. Reynolds Number (Fluid Mechanics): \\
   \( Re = \frac{\rho \cdot v \cdot D}{\mu} \) \\
4. Nusselt Number (Convection Heat Transfer): \\
   \( Nu = \frac{h \cdot L}{k} \) \\
5. Fourier's Law (Heat Conduction): \\
   \( q = -k \cdot A \cdot \frac{dT}{dx} \) \\
6. Diffusion Equation (Mass Transfer): \\
   \( \frac{\partial C}{\partial t} = D \cdot \nabla^2 C \) \\
7. Euler's Formula (Buckling of Columns): \\
   \( F_{\text{critical}} = \frac{\pi^2 \cdot E \cdot I}{(K \cdot L)^2} \) \\
8. Carnot Efficiency (Ideal Heat Engine): \\
   \( \eta_{\text{Carnot}} = 1 - \frac{T_{\text{low}}}{T_{\text{high}}} \) \\
9. Law of Conservation of Linear Momentum: \\
   \( \Sigma F = m \cdot a \) \\
10. Law of Conservation of Angular Momentum: \\
    \( \Sigma \tau = I \cdot \alpha \) \\
11. Law of Conservation of Energy: \\
    \( \Sigma W = \Delta KE + \Delta PE + Q \) \\
12. Pascal's Law (Hydrostatic Pressure): \\
    \( \Delta P = \rho \cdot g \cdot \Delta h \) \\
13. Stokes' Law (Viscous Drag on a Sphere): \\
    \( F_d = 6 \cdot \pi \cdot \mu \cdot R \cdot v \) \\
14. Strouhal Number (Flow past a Cylinder): \\
    \( St = \frac{f \cdot D}{v} \) \\
15. Capacitance (Parallel Plate Capacitor): \\
    \( C = \frac{\varepsilon_0 \cdot A}{d} \) \\
16. Inductance (Solenoid): \\
    \( L = \frac{\mu_0 \cdot N^2 \cdot A}{l} \) \\
17. Biot-Savart Law (Magnetic Field around a Wire): \\
    \( dB = \frac{\mu_0 \cdot I \cdot dl \times r}{4 \cdot \pi \cdot r^3} \) \\
18. Displacement Current (Maxwell's equations): \\
    \( \frac{\partial D}{\partial t} = \nabla \times H \) \\
19. Resistivity (Electrical Resistance): \\
    \( \rho = R \cdot \frac{A}{L} \) \\
20. Force on a Current-Carrying Wire in a Magnetic Field: \\
    \( F = I \cdot L \times B \) \\
21. Speed of Sound in a Gas: \\
    \( v = \sqrt{\gamma \cdot R \cdot T} \) \\
22. Specific Heat Capacity: \\
    \( Q = mc\Delta T \) \\
23. Coefficient of Performance (Refrigeration Cycle): \\
    \( \text{COP} = \frac{Q_{\text{in}}}{W_{\text{in}}} \) \\
24. Heat Transfer by Radiation (Stefan-Boltzmann Law): \\
    \( q = \sigma \cdot A \cdot (T_h^4 - T_c^4) \) \\
25. Snell's Law (Refraction of Light): \\
    \( n_1 \cdot \sin(\theta_1) = n_2 \cdot \sin(\theta_2) \) \\
\newpage
\vfill\eject
\section*{Ambiguous Variables}


F \\

    Newton's Second Law: Force \\
    Coulomb's Law: Electrostatic Force \\
    Euler's Formula: Critical Load \\
    Law of Conservation of Linear Momentum: Net Force \\

T \\

    Ideal Gas Law: Temperature \\
    Torsional Shear Stress: Torque \\

P \\

    Work Done by a Force: Power \\
    Pressure in a Fluid at Rest: Pressure \\

v \\

    Kinetic Energy: Velocity \\
    Fluid Flow Rate: Velocity \\
    Reynolds Number: Velocity \\
    Speed of Sound in a Gas: Velocity \\

Q \\

    Efficiency (Thermal): Heat \\
    Law of Conservation of Energy: Heat \\
    Specific Heat Capacity: Heat \\
    Heat Transfer by Radiation: Heat \\

A \\

    Bernoulli's Equation: Area \\
    Capacitance: Area \\

L \\

    Law of Conservation of Linear Momentum: Length \\
    Inductance: Length \\
    Displacement Current: Length \\

R \\

    Ohm's Law: Resistance \\
    Resistivity: Resistance \\

I \\

    Hooke's Law: Spring Constant \\
    Bernoulli's Equation: Current \\
    Capacitance: Current \\
    Biot-Savart Law: Current \\

E \\

    Young's Modulus: Elastic Modulus \\
    Euler's Formula: Modulus of Elasticity \\

h \\

    Potential Energy: Height \\
    Moment of Inertia: Height \\
\end{multicols}
\end{document}
